### 2018-08-07 paper/related.tex
taking away related work on prediction, contrasting with replication

Onion routing, with infrastructure and governance (Tor) and without (I2P), are geared toward web browsing. \sonja{will expand and cite}

\sonja*{include some on Modeling devices' connection and disconnection}

%\commentAL{Will need another pass.}
%\paragraph*{Modeling devices' connection and disconnection} 
% To simulate users' devices participating in a distributed protocol, we build upon existing literature on two topics: 
% multi-device interaction, and churn in P2P networks.

%In our experiments, we simulate users' devices participating in a distributed protocol. We base our modeling of devices' online availability on existing literature such as the following.  
% Field studies provide \emph{usage and connectivity patterns of users' appliances}. Karlson et al. \cite{Karlson_Meyers_Jacobs_Johns_Kane_2009} studied the compared usage of the laptop and smartphone of 16 information workers and show that their participants use their smartphones very regularly throughout the day to do background tasks (\eg answering mails or checking their agenda). Their laptop is online less often, and is dedicated to the most demanding tasks. Wagner et al. \cite{Wagner_Rice_Beresford_2013} conducted a thorough data collection on Android devices via an application called Device Analyzer, that collected metrics on movement patterns, connectivity and energy consumption from 16,000 users.
% %\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}
% Several works point out the emerging trend of \emph{multi-device interaction}.
% A 2012 Google-led study \cite{google2012} stated that the USA are nowadays ``a nation of multi-screeners''. People switch their attention toward their phone, laptop, tablet or their television depending on the context.
% M\"uller et al. \cite{Muller_Gove_Webb_Cheang_2015} specifically compared the usage patterns of phones against tablets.
% Jokela et al. \cite{Jokela_Ojala_Olsson_2015} and \cite{google2012} also differentiated sequential and parallel usage of one's multiple devices.
% Research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).
% We take inspiration from these works in order to establish credible models of user behaviors to evaluate our protocol. 
% Participants can own several devices: their smartphone is always on, but lacks processing power, while their laptop is rarely online, though it contains better hardware, etc.

>>>>

Onion routing schemes, with infrastructure and governance (Tor~\cite{Tor}) and without (I2P~\footnote{https://geti2p.net/en/}), though geared toward web browsing, come closest to file transfer without third-party storage. They do not, however, allow for unreliable user devices as relay nodes.

The main concern, shared with traditional P2P file sharing, is churn~\cite{dhtchurn} and its effect on availability. % - here in the narrow context of the set of user devices based on user behavior. 
The commonly used approach of replication and redundancy used to handling churn does not work in our case as we prioritize privacy and independence from third-party storage.

% We thus discuss the related work on modeling and predicting device availability next, though to the best of our knowledge we are the first to make use of such predictions to cope with churn in interoperating sets of user devices.

% %\sonja*{include some on Modeling devices' connection and disconnection}

% %\commentAL{Will need another pass.}
% %\paragraph*{Modeling devices' connection and disconnection} 
% To simulate users' devices participating in a distributed protocol, we build upon existing literature on two topics: 
% multi-device interaction, and churn in P2P networks.

% In our experiments, we simulate users' devices participating in a distributed protocol. We base our modeling of devices' online availability on existing literature such as the following.  
% Field studies provide \emph{usage and connectivity patterns of users' appliances}. Karlson et al. \cite{Karlson_Meyers_Jacobs_Johns_Kane_2009} studied the compared usage of the laptop and smartphone of 16 information workers and show that their participants use their smartphones very regularly throughout the day to do background tasks (\eg answering mails or checking their agenda). Their laptop is online less often, and is dedicated to the most demanding tasks. Wagner et al. \cite{Wagner_Rice_Beresford_2013} conducted a thorough data collection on Android devices via an application called Device Analyzer, that collected metrics on movement patterns, connectivity and energy consumption from 16,000 users.
% %\commentAL{Conclude: will we use their dataset? Why are these papers useful to us?}
% Several works point out the emerging trend of \emph{multi-device interaction}.
% A 2012 Google-led study \cite{google2012} stated that the USA are nowadays ``a nation of multi-screeners''. People switch their attention toward their phone, laptop, tablet or their television depending on the context.
% M\"uller et al. \cite{Muller_Gove_Webb_Cheang_2015} specifically compared the usage patterns of phones against tablets.
% Jokela et al. \cite{Jokela_Ojala_Olsson_2015} and \cite{google2012} also differentiated sequential and parallel usage of one's multiple devices.
% Research in P2P networks observed \cite{Stutzbach_Rejaie_2006} and modeled \cite{Yao_Leonard_Wang_Loguinov_2006} patterns of \emph{churn} (\ie participants moving in and out of a system).
% We take inspiration from these works in order to establish credible models of user behaviors to evaluate our protocol. 
% Participants can own several devices: their smartphone is always on, but lacks processing power, while their laptop is rarely online, though it contains better hardware, etc.
